Testing some bootstrap process

### 2024-08-02 test_boot_short_3.Rmd
Alternative bootstrap method ready to knit

---
title: "Testing some bootstrap process"
output: pdf_document
date: "2024-07-31"
---

@@

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/5 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (900/899)*sum(unlist(df[,4 + (5*(c-1))])/p))
    vec_est2 <- append(vec_est2, (900/899)*sum(unlist(df[,5*c])/p))
    vec_est3 <- append(vec_est3, ((900/899)*sum(unlist(df[,5*c])/p))/((900/899)*sum(unlist(df[,4 + (5*(c-1))])/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

@@

    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))

    # Confidence intervals
    norm_CI <- data.frame(useless = rep(0, 2))
    perc_CI <- data.frame(useless = rep(0, 2))
    rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:3) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    norm_CI$useless <- NULL
    perc_CI$useless <- NULL
    rev_perc_CI$useless <- NULL
    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

>>>>

---
title: "Testing some bootstrap process"
output: pdf_document
date: "2024-08-02"
---

@@

  n <- nrow(df) + 100 # sample size of the initial sample
  nboot <- length(df)/5 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (1/100)*(1000/9)*sum(as.vector(unlist(df[,4 + (5*(c-1))]))/p))
    vec_est2 <- append(vec_est2, (1/100)*(1000/9)*sum(as.vector(unlist(df[,5*c]))/p))
    vec_est3 <- append(vec_est3, ((1000/9)*sum(as.vector(unlist(df[,5*c])/p)))/((1000/9)*sum(as.vector(unlist(df[,4 + (5*(c-1))]))/p)))
    # (n_h/(n_h-1))*(n/n_h) is the correction needed since we choose only (n_h-1) points per strata
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

@@

    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))
    est_b <- as.vector(est_b)

    # Confidence intervals
    norm_CI <- data.frame(useless = rep(0, 2))
    perc_CI <- data.frame(useless = rep(0, 2))
    rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:3) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l]*2 - lim_sup, est_b[l]*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    norm_CI$useless <- NULL
    perc_CI$useless <- NULL
    rev_perc_CI$useless <- NULL
    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```
